Circumcision Paper Text

### 2024-04-15 paper/paper_cals.Rmd
Section 5 completed!

## Subnational Variation in Total, Medical \& Traditional Circumcision over time

@@

## Subnational Variation in total, medical \& traditional circumcision across different ages

@@

## Subnational Heterogeneity in Age at Medical and Traditional Circumcision

@@

## Decrease in TMC in SSA region Over Time

@@

## UNAIDS Goals Progress amongst 10-29 Year Olds in VMMC Target Countries

@@

This equates to 
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
(
`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
 to 
`n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
)
and 
`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
(
`n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
to
`n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
)
times the projected number of MCs for 10-29 and 15-49 year olds for 2020. 
The largest increase in MC coverage amongst VMMC priority countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
x
, from 
x
\% (
x
\% to 
x
\%) in 2006 to 
x
\% (
x
\% to 
x
\%) in 2020, a 
x
\% (
x
\% to 
x
\%) increase.

However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries.

x
/
x
 districts in these countries were e
x
pected to have reached 90\% MC coverage amongst 10-29 year olds in 2020, up from 
x
/
x
 in 2006, before VMMC programmes began. 
Even in 
x
, where MC was projected to be lowest in 2020, 
x
/
x
 districts were forecasted to have reached 90\% MC coverage for men aged 10-29 years old. 
MC coverage there increased from 
x
(
x
to 
x
) in 2006 to 
x
(
x
to 
x
) in 2020, a 
x
(
x
to 
x) increase.

>>>>

## Subnational variation in total, medical \& traditional circumcision over time

@@

## Subnational variation in total, medical \& traditional circumcision across different ages

@@

## Subnational heterogeneity in age at medical and traditional circumcision

@@

## Decrease in traditional male circumcision in SSA region over time

@@

## UNAIDS goals progress amongst 10-29 year olds in VMMC target countries

@@

This equates to 
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(mean_diff)`
(
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(lower_diff)`
 to 
`r n_required_vmmc %>% filter(age_group == "10-29") %>% pull(upper_diff)`
)
and 
`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
(
`r n_required_vmmc %>% filter(age_group == "15-49") %>% pull(mean_diff)`
to
`r n_required_vmmc %>% filter(age_group == "15-") %>% pull(mean_diff)`
)
times the projected number of MCs for 10-29 and 15-49 year olds for 2020.

MC coverage in 2020 for 10-29 year olds in VMMC priority countries was highest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
), and lowest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
.
For 15-49 year olds, the highest MC coverage was in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
), and lowest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
.
MMC coverage for 10-29 year olds in VMMC priority countries was highest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
), and lowest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
.
For 15-49 year olds, the highest MMC coverage was in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(1) %>% pull(upper) %>% to_percentage()`
), and lowest in 
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(iso3) %>% to_cntry_name()`,
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(mean) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(lower) %>% to_percentage()`
`r largest_smallest_vmmc %>% filter(year == 2020, type == "MMC", age_group == "10-29") %>% slice(n()) %>% pull(upper) %>% to_percentage()`
.

The largest increase from 2006 to 2020 in MC coverage for 10-29 year olds amongst VMMC priority countries was in 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(iso3) %>% to_cntry_name()`, 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
) increase. 
In contrast, the lowest increase in MC coverage in these countries was in 
from 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2006) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_2006) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_2006) %>% to_percentage()`
) in 2006 to 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_2020) %>% to_percentage()`
) in 2020, a 
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(mean_diff) %>% to_percentage()`
(
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(lower_diff) %>% to_percentage()`
-
`r increase_vmmc %>% filter(type == "MC", age_group == "10-29") %>% slice(1) %>% pull(upper_diff) %>% to_percentage()`
) increase.

However, these figures belie significant subnational heterogeneity in MC coverage amongst VMMC priority countries. 
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
(
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
-
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
)
of
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2020) %>% summarise(sum(n)) %>% pull()`
districts in these countries were expected to have reached 90\% MC coverage 
amongst 10-29 year olds in 2020, up from 
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
(
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
-
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
) of
`r cntry_districts_thresh %>% filter(age_group == "10-29", year == 2006) %>% summarise(sum(n)) %>% pull()`
in 2006, before VMMC programmes began. 
Similarly, 
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(mean_indicator)) %>% pull()`
(
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(lower_indicator)) %>% pull()`
-
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(upper_indicator)) %>% pull()`
)
of
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2020) %>% summarise(sum(n)) %>% pull()`
districts in these countries were expected to have reached 80\% MC coverage for 
15-49 year olds in 2020, compared to
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(mean_indicator)) %>% pull()`
(
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(lower_indicator)) %>% pull()`
-
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(upper_indicator)) %>% pull()`
) of
`r cntry_districts_thresh %>% filter(age_group == "15-49", year == 2006) %>% summarise(sum(n)) %>% pull()`
in 2006.

In 2020, 
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(mean)`
(
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(lower)`
-
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "10-29") %>% pull(upper)`
)
of the 14 VMMC priority countries had no districts which satisfied the 90\% MC coverage target for 10-29
year olds. This was down from 
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(mean)`
(
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(lower)`
-
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "10-29") %>% pull(upper)`
)
in 2006. 
Similarly, in 2020, 
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(mean)`
(
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(lower)`
-
`r n_cntries_no_thresh %>% filter(year == 2020, age_group == "15-49") %>% pull(upper)`
)
countries had no districts which satisfied the 80\% MC coverage target for 15-49
year olds. This was down from 
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(mean)`
(
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(lower)`
-
`r n_cntries_no_thresh %>% filter(year == 2006, age_group == "15-49") %>% pull(upper)`
)
in 2006.
